\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.5in,nofoot]{geometry}
\usepackage{fontawesome5}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,
    urlcolor=blue,
    citecolor=blue
}

\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule]
\titlespacing*{\section}{0pt}{*1}{*1}

\newcommand{\entry}[4]{
  \noindent\textbf{#1} \hfill #2 \\
  \noindent\textit{#3} \hfill \textit{#4} \\
  \vspace{2pt}
}

\newcommand{\project}[2]{
  \noindent\textbf{#1} \hfill #2 \\
  \vspace{2pt}
}

\begin{document}

\pagenumbering{gobble}

\noindent
\begin{minipage}[t]{0.5\textwidth}
\textbf{\Large João Pedro Tentis}

\vspace{0.4em}

\noindent \faMapMarker ~ Rio de Janeiro, RJ - Jacarepaguá ~ \faUser ~ 25 years old \\
\end{minipage}%
\begin{minipage}[t]{0.5\textwidth}
\raggedleft
{\color{blue}} {\faPhone \space +55 21 992285653} \quad
{\color{blue}} \href{mailto:jps.tentis@gmail.com}{\faEnvelope \space jps.tentis@gmail.com}

\vspace{0.2em}

{\color{blue}} \href{https://joaotentis.dev}{\space joaotentis.dev}
{\color{blue}} \href{https://github.com/jtentis}{\faGithub \space GitHub} \quad
{\color{blue}} \href{https://linkedin.com/in/jtentis}{\faLinkedin \space LinkedIn} \\
\end{minipage}

\vspace{0.5em}

\section*{Experience}
\vspace{0.6em}
\entry{Di Santinni}{\faCalendar \space 03/2025 -- Present}{Systems Analyst}{\faMapMarker \space Remote}
\vspace{-1.6em}
\begin{itemize}
\setlength\itemsep{-0.3em}
\item Responsible for the maintenance and evolution of the company's internal system, ensuring efficient operation and meeting user demands.
\item Oracle database management, focusing on performance, SQL query development, report extraction, and system integration.
\item Development of middleware solutions using Python (Flask, FastAPI, and WebScraping) and Node.js for XML file processing and external API consumption, converting file inputs into API requests.
\end{itemize}

\entry{Viva Rio}{\faCalendar \space 01/2024 -- 03/2025 (\textbf{$\sim$ 1 yr 2 mos})}{Information Assistant I}{\faMapMarker \space On-site}
\vspace{-1.6em}
\begin{itemize}
\setlength\itemsep{-0.3em}
\item Development of a desktop WhatsApp bot using Node.js with Nest.js, Electron.js, TypeScript, and TailwindCSS.
\item Development, customization, and deployment of an LMS platform (EAD) on HostGator using Moodle, PHP, and SCSS.
\item Creation of dynamic Dashboards with PowerBI, using Excel VBA and Python.
\item Microservices architecture and unit testing implementation.
\end{itemize}

\entry{Di Santinni}{\faCalendar \space 02/2022 -- 01/2024 (\textbf{$\sim$ 1 yr 11 mos})}{IT Intern}{\faMapMarker \space Remote}
\vspace{-1.6em}
\begin{itemize}
\setlength\itemsep{-0.3em}
\item Service automation utilizing Python and pyautogui.
\item Spreadsheet control and management using Excel and Google Sheets.
\end{itemize}

\entry{Global Hitss}{\faCalendar \space 10/2020 -- 02/2022 (\textbf{$\sim$ 1 yr 3 mos})}{Computer Operator}{\faMapMarker \space Remote}
\vspace{-1.6em}
\begin{itemize}
\setlength\itemsep{-0.3em}
\item Process automation utilizing Python web scraping.
\item Spreadsheet management using Excel.
% \item Documentation control of outsourced services in the intranet system.
\end{itemize}

% \entry{Globo}{\faCalendar \space 03/2019 -- 05/2020 (\textbf{$\sim$ 1 yr 2 mos})}{Apprentice - Administrative Assistant}{\faMapMarker \space On-site}
% \vspace{-1.6em}
% \begin{itemize}
% \setlength\itemsep{-0.3em}
% \item Order requests for scenic cities.
% \item General production stock control.
% \item Preparation, translation, and presentation of meetings in English for foreign suppliers.
% \end{itemize}

\section*{Projects}
\vspace{0.6em}
\project{\href{https://github.com/jtentis/MatchMovie-Native}{\space Match Movie} | \normalfont{\textit{React Native, TypeScript, EXPO, Node.js, Nest.js, PostgreSQL}}}{\textbf{February 2025}}
\vspace{-1.6em}
\begin{itemize}
\setlength\itemsep{-0.3em}
\item Development of a \textit{tinder-like} application (Bachelor's Thesis project) to facilitate movie choices for groups of users.
\item Integration of external APIs such as TheMovieDB, OpenCage Geocoding, and Ingresso.com; usage of technologies like Context API, Expo Secure Store, and React Navigation.
\item Redirection to nearby movie theaters based on user location.
\item Screens designed with UI/UX standards, responsive and engaging interface, focusing on user experience.
\end{itemize}

\project{\href{https://github.com/jtentis/HorseCare}{\space HorseCare} | \normalfont{\textit{PHP, JavaScript, HTML, CSS, MySQL}}}{\textbf{December 2023}}
\vspace{-1.6em}
\begin{itemize}
\setlength\itemsep{-0.3em}
\item Development of an application for horse boarding management.
\item User and employee registration with login authentication.
% \item Responsive interface, developed with Figma following UI/UX standards.
\end{itemize}

\project{\href{https://www.linkedin.com/company/obinvestbrasil/}{\space Commodities} | \normalfont{\textit{Python, Streamlit, CSS}}}{\textbf{June 2023}}
\vspace{-1.6em}
\begin{itemize}
\setlength\itemsep{-0.3em}
\item Development of a Streamlit application for commodity and asset analysis/variance, utilizing matplotlib and pandas.
\item Developed in partnership with \href{https://www.linkedin.com/company/obinvestbrasil/}{\space OBInvest} (Brazilian Investment Olympiad).
% \item Extraction of asset and commodity information using yfinance.
\end{itemize}

\section*{Education}
\vspace{0.6em}
\entry{CEFET}{\faCalendar \space 02/2021 -- 02/2025 (\textbf{$\sim$ 4 years})}{Bachelor of Information Systems}{\faMapMarker \space On-site}
\vspace{0.6em}

\section*{Skills}
\vspace{0.6em}
\begin{itemize}
\item \textbf{Languages:} \textbf{Native}: Portuguese | \textbf{Advanced}: English (C2 Level) | \textbf{Basic}: Spanish
\item \textbf{Technologies:} JavaScript, TypeScript, HTML, CSS, Excel, Python, Node.js, PostgreSQL, Oracle, MariaDB, MySQL, MongoDB
\item \textbf{Tools:} Git, GitHub, VSCode, Docker, HostGator, Vercel, AWS (Lambda, S3, EC2), CloudFlare, Railway, Cpanel, Figma, Trello, Jest, Playwright, SOLID
\item \textbf{Frameworks:} Nest.js, Electron.js, Express, React, React Native, Expo, Swagger, TailwindCSS, SCSS, VBA, Pandas, Streamlit, Flask, FastAPI
\end{itemize}

\end{document}